---
title: ' Refugees'
author: "Vivek Mangipudi"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: no
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}

library(ggplot2)
library(readr)
library(leaflet)
library(knitr)
library(highcharter)
library(plyr)
library(dplyr)
library(tidyr)
library(viridis)
library(plotly)
library(tidyr)
library(maps)
library(ggmap)
library(gridExtra)
library(countrycode)
library(stringr)
library(tidyverse)
library(maps)
library(geosphere)
library(ggmap)
library(maptools)
library(networkD3)
library(d3Network)

ASM <- read_csv("../cleaned_data/cleaned_asylum_seekers_added.csv")
resettlement <- read_csv("../cleaned_data/cleaned_asylum_seekers_added.csv")
```
     
   
  
 
```

Add Introduction later  



**All plots are interactive**    


# Country of Origin 

From Which country of Origin have the most number of refugees originated?  

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8 , fig.height = 6}
ASM %>% 
  select(Origin,Total.decisions) %>% 
  group_by(Origin) %>% 
  summarise(Total = sum(Total.decisions, na.rm = T)) -> ASM_byorg

ASM_byorg<- arrange(ASM_byorg, -Total)

hchart(ASM_byorg[1:20,], "column", hcaes(`Origin`, y = Total, color = Total)) %>%
  hc_colorAxis(stops = color_stops(n = 6, colors = c( "#21908C", "#04eadf","#440154"))) %>%
  hc_add_theme(hc_theme_db()) %>%
  hc_title(text = "Countries from which most refugees originate : ") %>%
  hc_credits(enabled = TRUE, text = "Data Source: UNHCR ", style = list(fontSize = "12px")) %>%
  hc_legend(enabled = FALSE)

``` 
<br>  

 
` 
```

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10 , fig.height = 10, eval = FALSE}

maps::map('world',col="#b5bebf", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-100,100) )
# long lat ; NE will be +ve SW will -ve
Syria = c(38.9968, 34.8021)
Afghanistan = c(67.7100, 33.9391)
Canada = c(-106.3468, 56.13037)
USA = c( -95.7129, 37.0902)
UK = c(-3.4360,55.3781)
Norway = c(8.4689, 60.4720)
Australia = c(133.7751,- 25.2744)
Sweden = c( 18.6435,60.128)
Finland = c(25.7482 , 61.9241)

data=rbind(Syria,Afghanistan, Canada, USA, UK , Norway, Australia, Sweden , Finland) %>% as.data.frame()
colnames(data)=c("long","lat")
points(x=data$long, y=data$lat, col="slateblue", cex=1, pch=20)
text(rownames(data), x=data$long, y=data$lat,  col="black", cex=1, pos=4)


#Adding lines between the  points :
# namz<- c("Canada" , "USA", "UK", "Australia")
namz<-rownames(data)
colz<-c("2bdcef", "slateblue" , "#1acfdd" , "black","#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00", "#CAB2D6", "#6A3D9A", "#B15928")

# for (i in 1:4){
#   inter <- gcIntermediate(Syria, namz[i], n=100, addStartEnd=TRUE, breakAtDateLine=F)             
#   lines(inter, col= colz[i], lwd=5)
#   
# }

#Syria great circles
mymap<- function(x,y,z){
  inter <- gcIntermediate(Syria, x, n=100, addStartEnd=TRUE, breakAtDateLine=F)             
  lines(inter, col= y, lwd=z)
     }

# for(i in 2: 5){
#   mymap(namz[i],colz[i], 5-i )
# }

mymap(Canada, "#1192a0", 4)
mymap(USA, "#1192a0", 2)
mymap(UK, "#1192a0", 2)
mymap(Norway, "#1192a0", 2)
mymap(Australia, "#1192a0", 2)
mymap(Sweden, "#1192a0", 2)
mymap(Finland, "#1192a0", 2)
#mymap(Finland, "slateblue", 2)




#Afghanistan

mymapaf<- function(x,y,z){
  inter <- gcIntermediate(Afghanistan, x, n=100, addStartEnd=TRUE, breakAtDateLine=F)             
  lines(inter, col= y, lwd=z)
  
}

# for(i in 2: 5){
#   mymap(namz[i],colz[i], 5-i )
# }



mymapaf(Canada, "#41037f", 2)
mymapaf(USA, "#41037f", 2)
mymapaf(UK, "#41037f", 2)
mymapaf(Norway, "#41037f", 2)
mymapaf(Australia, "#41037f", 2)
mymapaf(Sweden, "#41037f", 2)
mymapaf(Finland, "#41037f", 2)

```

  
###  Congo Iraq Refugee Resettlement Movements  


```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10 , fig.height = 10}

 
SWE = c( 18.6435,60.128)
Ger = c(10.4515, 51.1657)
Iraq = c(43.6793 , 33.2232)
Neth = c(5.2913,52.1326)
Turkey = c(35.2433,38.9637)

congo = c(21.7587, 4.0383)
bun = c(29.9189, 3.3731)
rwanda = c(29.8739, 1.9403)
uganda = c(32.2903,1.3733)
kenya = c(37.9062, 0.0236)

#main plotting
maps::map('world',col="#b5bebf", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-100,100) )
data=rbind(SWE, Ger, Iraq, Neth, Turkey, congo, bun , rwanda, uganda, kenya) %>% as.data.frame()
colnames(data)=c("long","lat")
points(x=data$long, y=data$lat, col="slateblue", cex=1, pch=20)
text(rownames(data), x=data$long, y=data$lat,  col="black", cex=0.6, pos=3)

#Irag great circles

mymap<- function(x,y,z){
  inter <- gcIntermediate(Iraq, x, n=100, addStartEnd=TRUE, breakAtDateLine=F)             
  lines(inter, col= y, lwd=z)
    }


mymap(SWE, "#1192a0", 2)
mymap(Ger, "#1192a0", 1)
mymap(Neth, "#1192a0", 1)
mymap(Turkey, "#1192a0", 1)
 
#mymap(Finland, "slateblue", 2)


# Iraq 

mymapir<- function(x,y,z){
  inter <- gcIntermediate(congo, x, n=100, addStartEnd=TRUE, breakAtDateLine=F)             
  lines(inter, col= y, lwd=z)
}
mymapir(kenya, "#ef2a9a", 1)
mymapir(uganda, "#ef2a9a", 1)
mymapir(rwanda, "#ef2a9a", 1)
mymapir(bun, "#ef2a9a", 1)
 
```
<br>


### Afghanistan Ukraine Refugees Resettlement Movements

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10 , fig.height = 10}

Afghanistan = c(67.7100, 33.9391)
SWE = c( 18.6435,60.128)
UK = c(-3.4360,55.3781)
Ger = c(10.4515, 51.1657)
AUS = c(14.5501, 47.5162)
 
 
Ukr = c(31.1656, 48.3794)
Rus = c(105.3188 , 61.5240)

#main plotting
maps::map('world',col="#b5bebf", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-100,100) )
data=rbind(Ger,Afghanistan, UK , AUS, SWE ,Ukr,Rus) %>% as.data.frame()
colnames(data)=c("long","lat")
points(x=data$long, y=data$lat, col="slateblue", cex=1, pch=20)
text(rownames(data), x=data$long, y=data$lat,  col="black", cex=0.6, pos=3)




#Afghanistan
mymapaf<- function(x,y,z){
  inter <- gcIntermediate(Afghanistan, x, n=100, addStartEnd=TRUE, breakAtDateLine=F)             
  lines(inter, col= y, lwd=z)
  }

mymapaf(Ger, "#41037f", 1)
 
mymapaf(UK, "#41037f", 1)
 
mymapaf(AUS, "#41037f", 1)
mymapaf(SWE, "#41037f", 1)
 
#mymap(Finland, "slateblue", 2)



# ukraine
mymapchn<- function(x,y,z){
  inter <- gcIntermediate(Ukr, x, n=100, addStartEnd=TRUE, breakAtDateLine=F)             
  lines(inter, col= y, lwd=z)
}
mymapchn(Rus, "#b29d01", 1)
 

``` 

  
```

Can I make map plots more pretty?  Hmm. . .


# Network Graphs

### Simple Interactive Force Directed Graphs on Resettlements    


***The network graph below is interactive. Feel free to drag push and pull the countries here and there, to best suit your needs.  ***


```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10 , fig.height = 10}

simpleNetwork(acc_by_country_all[,1:2] , fontSize = 12, zoom = T , linkDistance = 150)

```     

This network plot is based on the resettlement.csv file.  

After dragging the graph to make it wider, Hover on a node, say Iraq and you can see all the countries in which Iraqi Refugees were provided resettlement.    

As you can see,   
* Syria Refugees who were given resettlement went mostly to CANADA and USA , or to one of the European Countries.  
* It is such a pity that there is no trace of any of the rich Middle Eastern countries providing resettlement to the refugees. (Atleast based on this data)   
*   


<br>

### Sankey Plot Resettlements of Refugees from Syria Afghanistan Iraq China

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10 , fig.height = 10}

resettlement %>% 
  filter(Origin == "Dem. Rep. of the Congo" |Origin == "Afghanistan"|Origin == "Iraq" |Origin == "Ukraine") %>% 
  select(Origin , Successful , `Country / territory of asylum/residence`) %>% 
  rename(source =  Origin, target = `Country / territory of asylum/residence`) %>% 
  group_by(source, target) %>%
  na.omit() %>% 
  dplyr::summarize(value = sum(Successful)) %>% 
  filter(value>18000)-> Sank_usa

Nodes <-rbind(data.frame(name = unique(Sank_usa$source)), data.frame(name = unique(Sank_usa$target)))
Links <- Sank_usa
Links$source <- match(Links$source, Nodes$name) - 1
Links$target <- match(Links$target, Nodes$name) - 1

require(d3Network)

sankeyNetwork(
  Links = Links,
  Nodes = Nodes,
  Source = "source",
  Target = "target",
  Value = "value",
  NodeID = "name",
  nodeWidth = 60,
  fontSize = 15
)

```

#

To do , explore remaining data sets here.      



**Leave an upvote if you like what you see.  **  

 